Supermartingales and Termination Analysis of Statistical PCF

### 2021-01-10 LICS21/related.tex
Introduce Conjecture environment for the completeness conjecture.

\label{sec:related}
We have not yet been able to prove our conjecture that every term is antitone rankable if all of the terms reachable from it are AST, which would imply that \Cref{thm:antitone rankable implies termination} is almost complete.

>>>>

\label{sec:related}
We have not yet been able to prove \Cref{conj:antitone} which would imply that \Cref{thm:antitone rankable implies termination} is almost complete.
\begin{conjecture}
\label{conj:antitone}
Every term is antitone rankable if all of the terms reachable from it are AST.
\end{conjecture}
